---
title: "HSteacher"
author: "Chenyang James Wang"
co-author: "Donghun Louis Lee"
date: 22/28/2018"
output:
  html_document: default
  pdf_document: default

---
```{r global_options, include=FALSE, results='asis'}

```

inta
```{r setup, include=FALSE}
#setwd("~/Dropbox/BassConnectionsRAs/HS Survey/")
library(raster)
library(readr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(stringr)
library(descr) 
library(foreign)
library(haven)
library(knitr)
library(xtable)
#hs = read_csv("1HSPrincipals_012218.csv")
# hs = haven::read_spss("HSPrincipals_01292018.sav")
#hs_labeled= read.csv("High+School+Civic+Indicators+-+Principals_February+24%2C+2018_14.45.csv", stringsAsFactors = T,na.strings = "")
hs_labeled= read_csv("High+School+Civic+Indicators+-+Principals_February+24%2C+2018_14.45.csv")
hs=hs_labeled[3:nrow(hs_labeled),]
hs=hs_labeled[-c(1,2),]
View(hs)
```

### Student government voting categorization
```{r}

# hs$stugov_vote %>% table()
hs$stugov_vote_categorized <- NA
# very good: 95 +
hs$stugov_vote_categorized[hs$stugov_vote >=95] <- "95+"
# good : 90+
hs$stugov_vote_categorized[hs$stugov_vote< 95 & hs$stugov_vote >=90 ] <- "90-95"
# slightly good:85+
hs$stugov_vote_categorized[hs$stugov_vote < 90 & hs$stugov_vote >=85] <- "85-89"
# okay: 80+
hs$stugov_vote_categorized[hs$stugov_vote < 85 & hs$stugov_vote >=80 ] <- "80-84"
# improving: 75+
hs$stugov_vote_categorized[hs$stugov_vote < 80 & hs$stugov_vote >=75 ] <- "75-79"
# not good: <75
hs$stugov_vote_categorized[hs$stugov_vote < 75 ] <- "<75"
hs$stugov_vote_categorized[is.na(hs$stugov_vote)] <- "NA"

hs$stugov_vote_categorized %>% table()
```

### all the one dim tables
```{r}

onetable_xtable = function(Q) {
   x = table(Q[1:length(Q)]) %>% prop.table() %>% round(2) 
   a <- xtable(x)
   print (a)
   #names(dimnames(x)) <- Q[[1]]
   #y <- names(dimnames(x)) <- Q[[1]]
   #print(paste("total count =", margin.table(countTable)))
}

nafunction = function(a) {
  a[is.na(a)] <- "NA"
  return (a)
}

hs$stugov_vote_categorized %>% onetable_xtable()
hs[[22]] %>% nafunction() %>% onetable_xtable()
hs[[23]] %>% nafunction() %>% onetable_xtable()
hs[[24]] %>% nafunction() %>% onetable_xtable()
hs[[25]] %>% nafunction() %>% onetable_xtable()
hs[[26]] %>% nafunction() %>% onetable_xtable()
hs[[27]] %>% nafunction() %>% onetable_xtable()
hs[[28]] %>% nafunction() %>% onetable_xtable()
hs[[34]] %>% nafunction() %>% onetable_xtable()
hs[[39]] %>% nafunction() %>% onetable_xtable()
hs[[52]] %>% nafunction() %>% onetable_xtable()
hs[[59]] %>% nafunction() %>% onetable_xtable()
hs[[64]] %>% nafunction() %>% onetable_xtable()

ct1 = function(x, y, xname = "X", yname = "Y", plot = F){
  crosstab(x, y,
           dnn = c(xname, yname),
           prop.r = TRUE,
           plot = plot, digits = 0, missing.include = FALSE, cell.layout = TRUE, drop.levels = TRUE)
}

#regdrive
hs$public %>% nafunction()
hs$regdrives %>% nafunction()
hs$courses %>% nafunction()
hs$parents_engaged %>% nafunction()
hs$skilldevleop %>% nafunction()

xtable(ct1(hs$public, hs$regdrives, xname= 'School', yname= 'regDrive', plot = F), caption = "School Type and regdrives?", label = "public school were more likely to be regdrives")

xtable(ct1(hs$public, hs$courses, xname= 'School', yname= 'Civic Course Yes or No', plot = F), caption = "School type and courses", label = "charter school had more civic courses provided")

#parents engagement
xtable(ct1(hs$public, hs$parents_engaged, xname= 'School', yname= 'Parents Engage', plot = F), caption = "School Type and Engagement of parents", label = "charter school parents were much more engaged ")

xtable(ct1(hs$stugov_vote_categorized, hs$parents_engaged, xname= 'Stugov Voting', yname= 'Parents Engage', plot = F), caption = "Student government voting and Engagement of parents", label = "no correlation")

#stu gov participation rate
xtable(ct1(hs$public, hs$stugov_vote_categorized, xname= 'School', yname= 'Student Vote', plot = F), caption = "School Type and student government voting", label = "charter school had signifincantly higher participation rate")

xtable(ct1(hs$stugov_vote_categorized, hs$courses, xname= 'Stugov Voting', yname= 'Civic Courses Yes or No', plot = F), caption = "student government voting and courses provided", label = "No significant relationship" ) 
#skill develop
xtable(ct1(hs$public,hs$skilldevleop, xname= 'School', yname= 'Skill Develop', plot = F), caption = "School type and skill development", label = "charter school had higher skill development ")







